%-------------------------
% Resume in Latex
% Author : Rajoli Girisai Madhav
% Based off of: https://github.com/jakeryang/resume
% License : MIT
% Final check Trigger workflow
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-44pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% RE-ENGINEERED FOR PERFECT SPACING CONSISTENCY
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}, itemsep=0pt, parsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=0pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{2pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Rajoli Girisai Madhav} \\ \vspace{5pt}
    \small\faPhone*~9121775542 \quad | \quad 
    \faEnvelope~\href{mailto:rajoligirisai.madhav@gmail.com}{rajoligirisai.madhav@gmail.com} \quad | \quad 
    \faLinkedin~\href{https://linkedin.com/in/rajoli-girisai-madhav}{linkedin.com/in/rajoli-girisai-madhav} \\ \vspace{2pt}
    \faGithub~\href{https://github.com/rajoli-girisai-madhav}{github.com/rajoli-girisai-madhav} \quad | \quad 
    \faGlobe~\href{https://rajoligirisaimadhav.online}{rajoligirisaimadhav.online}
    \\ \vspace{-3pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{PROFESSIONAL SUMMARY}
\noindent \textbf{AWS DevOps Engineer} with \textbf{3+ years of experience} in designing, automating, and managing \textbf{highly available cloud infrastructure on AWS}. Expertise in \textbf{Terraform (IaC)}, \textbf{GitHub Actions CI/CD}, \textbf{Docker}, and \textbf{cloud networking}. Proven track record in building \textbf{multi-tier, multi-region platforms} and serverless deployment pipelines that \textbf{reduced deployment time by 70\%+} while maintaining \textbf{99.9\% uptime}. Passionate about \textbf{infrastructure automation} and delivering reliable, scalable systems.

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}, itemsep=0pt, parsep=2pt]
    \small{\item{
     \textbf{Cloud \& IaC} {: AWS (EC2, VPC, S3, RDS, IAM, ALB, Auto Scaling, CloudFront, Route 53, WAF, ACM, SNS, Textract, Rekognition, Lex), Terraform (Modules, Workspaces, S3 Backend + State Locking), GitHub Actions CI/CD}\vspace{2pt} \\
     \textbf{Containers \& Orchestration} {: Docker, Kubernetes (Fundamentals)}\vspace{2pt} \\
     \textbf{Monitoring \& Observability} {: CloudWatch, AppDynamics}\vspace{2pt} \\
     \textbf{Scripting \& Version control} {: Bash/Shell Scripting, Git, GitHub}\vspace{2pt} \\
     \textbf{Databases} {: Oracle SQL, MySQL}\vspace{2pt} \\
     \textbf{Operating Systems} {: Linux, Unix, Stratus VOS}\vspace{2pt} \\
     \textbf{Tools \& Collaboration} {: JIRA, Confluence}\vspace{2pt} \\
     \textbf{Mainframe \& Legacy Systems} {: Mainframe/COBOL (Transaction Processing, Screen Maps), IBM DB2, File Processing, Operational Monitoring, Logging Mechanisms}
    }}
\end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{PROFESSIONAL EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AWS DevOps Engineer}{Aug 2025 -- Present}
      {Vcube Software Solutions}{Hyderabad, India}
      
      %--- Project 1 Header ---
      \vspace{2pt}
      \noindent\textbf{Project:} Production-Ready Multi-Region 3-Tier AWS Platform (Terraform + CI/CD) \\
      \small{\textbf{Tech Stack:} AWS, Terraform (IaC), GitHub Actions, CI/CD, VPC, EC2, ASG, ALB, Multi-AZ, S3 Remote Backend, Cloud Networking, Linux} \\
      \small{\textbf{GitHub:} \href{https://github.com/rajoli-girisai-madhav/aws-3tier-multi-region-terraform-platform}{https://github.com/rajoli-girisai-madhav/aws-3tier-multi-region-terraform-platform}}
      
      \resumeItemListStart
        \resumeItem{Designed a \textbf{multi-tier AWS architecture} using \textbf{Terraform}, enabling multi-region deployments across multi-AZ environments, ensuring fault tolerance and \textbf{99.9\% uptime}.}
        \resumeItem{Built \textbf{CI/CD pipelines} using \textbf{GitHub Actions matrix strategy}, automating deployments across dev, QA, and production environments with structured validation workflows.}
        \resumeItem{\textbf{Reduced deployment time by 70\%+} (under 15 minutes) through Infrastructure as Code (IaC), eliminating manual provisioning delays and improving delivery efficiency.}
        \resumeItem{Introduced \textbf{approval-based deployment controls} enhancing release governance, reducing production risks, and strengthening compliance across enterprise deployment workflows.}
        \resumeItem{Engineered AWS networking architecture including \textbf{VPC, subnets, route tables, and security groups}, enabling scalable compute using EC2, Auto Scaling Groups (ASG), and ALB.}
        \resumeItem{Implemented \textbf{S3 remote state management with locking mechanisms}, reducing configuration conflicts by \textbf{~60\%} and improving collaboration across engineering teams.}
        \resumeItem{Enabled \textbf{centralized logging and monitoring} improving system visibility, debugging efficiency, and proactive incident detection across environments.}
      \resumeItemListEnd

      %--- Project 2 Header ---
      \vspace{4pt}
      \noindent\textbf{Project:} Serverless CI/CD Pipeline for React Application (S3, Route 53, CloudFront, ACM \& WAF) \\
      \small{\textbf{Tech Stack:} AWS, GitHub Actions, CI/CD, Amazon S3, CloudFront, Route 53, AWS Certificate Manager (ACM), AWS WAF, AWS CLI, React, Serverless Hosting, DNS Management} \\
      \small{\textbf{GitHub:} \href{https://github.com/rajoli-girisai-madhav/react-aws-devops-portfolio}{https://github.com/rajoli-girisai-madhav/react-aws-devops-portfolio}}
      
      \resumeItemListStart
        \resumeItem{Built a fully automated \textbf{CI/CD pipeline} using \textbf{GitHub Actions}, enabling continuous build, test, and deployment workflows for frontend React applications.}
        \resumeItem{Hosted the application on \textbf{Amazon S3 integrated with CloudFront CDN}, ensuring scalable global content delivery with low-latency access.}
        \resumeItem{Configured \textbf{Route 53 domain routing} with custom domain mapping, enabling reliable traffic routing and production-grade DNS resolution.}
        \resumeItem{Enforced \textbf{HTTPS encryption using AWS Certificate Manager (ACM)}, securing application communication across edge and origin layers.}
        \resumeItem{Strengthened application security using \textbf{AWS WAF rules}, preventing unauthorized access attempts and protecting application endpoints.}
        \resumeItem{Automated deployments using \textbf{AWS CLI (S3 sync)} with version-controlled artifacts, ensuring consistent, repeatable, and traceable release processes.}
        \resumeItem{Implemented a \textbf{CloudFront cache invalidation strategy}, ensuring immediate propagation of updates without stale content delivery.}
      \resumeItemListEnd

    \resumeSubheading
      {Info Tech Senior Associate}{May 2022 -- Dec 2024}
      {NTT Data}{Bangalore, India}
      
      \resumeItemListStart
        \resumeItem{Automated operational workflows using \textbf{Bash/Shell scripting}, improving execution efficiency and reducing repetitive manual tasks.}
        \resumeItem{Built and maintained monitoring and alerting systems using \textbf{AppDynamics}, enabling proactive anomaly detection and faster incident response.}
        \resumeItem{Managed \textbf{high-volume production transaction systems} ensuring \textbf{99.9\% uptime} across mission-critical enterprise workloads.}
        \resumeItem{Reduced incident resolution time by \textbf{25--30\%} through structured \textbf{Root Cause Analysis (RCA)}, debugging, and proactive operational support.}
        \resumeItem{Ensured compliance with \textbf{Visa/MasterCard financial regulations}, maintaining secure and reliable transaction processing standards.}
        \resumeItem{Improved system stability, performance visibility, and operational reliability through continuous \textbf{production monitoring and observability} practices.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROFESSIONAL HIGHLIGHTS-----------
\section{PROFESSIONAL HIGHLIGHTS}
  \resumeItemListStart
    \resumeItem{\textbf{Cloud Infrastructure \& Automation:} Experienced in building highly available AWS infrastructure using Terraform, CI/CD automation, and cloud-native deployment workflows.}
    \resumeItem{\textbf{Production Operations:} Strong background in production operations, monitoring, and incident management across enterprise-scale systems.}
    \resumeItem{\textbf{Architecture Design:} Skilled in designing scalable multi-tier cloud architectures with a sharp focus on reliability, automation, and operational efficiency.}
    \resumeItem{\textbf{Networking \& Security:} Hands-on experience with cloud networking, security controls, and deployment governance across distributed environments.}
  \resumeItemListEnd

%-----------CERTIFICATIONS \& ACCOMPLISHMENTS-----------
\section{CERTIFICATIONS \& ACCOMPLISHMENTS}
  \resumeItemListStart
    \resumeItem{Mainframe Application Developer -- NTT DATA}
    \resumeItem{Financial Systems Certification -- NTT DATA}
    \resumeItem{SQL (Intermediate) -- HackerRank}
    \resumeItem{Performance Excellence Award -- 100\% SLA compliance}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {S.V. College of Engineering}{Sep 2017 -- Aug 2021}
      {Bachelor of Technology (B.Tech) -- Electrical and Electronics Engineering}{Chittoor, India}
  \resumeSubHeadingListEnd


\end{document}
